%% This is an example first chapter.  You should put chapter/appendix that you
%% write into a separate file, and add a line \include{yourfilename} to
%% main.tex, where `yourfilename.tex' is the name of the chapter/appendix file.
%% You can process specific files by typing their names in at the 
%% \files=
%% prompt when you run the file main.tex through LaTeX.
\chapter{Conclusions and Outlook}

Measurements of total inclusive and fiducial W and Z boson production cross sections at $\sqrt{s}=8~\TeV$  and $\sqrt{s}=13~\TeV$ center-of-mass energies are described. Muon and electron final states are considered in a data sample corresponding to an integrated luminosity of $18.2~\ipb$ at $8~\TeV$ and $43~\ipb$ at $13~\TeV$. A dilepton mass in the range of $60$ to $120~\GeV$ is required for the Z boson results. The measured total inclusive cross sections times branching fractions agree with next-to-next-to-leading-order QCD cross section calculations. Ratios of cross sections with a precision of $2\%$ are also reported. Indirect determination of the total $W$ boson width and $\mathcal{B}(W\rightarrow\ell\nu)$ is performed.

A search for a Standard Model Higgs boson decaying to a pair of tau leptons produced in proton-proton collisions at the Large Hadron Collider at $\sqrt{s}=7~\TeV$ and $\sqrt{s}=8~\TeV$ center-of-mass energies is described. Final states with at least one hadronic tau are described with a data sample collected with the CMS detector corresponding to an integrated luminosity of $19.7~\ifb$ at $8~\TeV$ and $4.9~\ifb$ at $7~\TeV$. A statistically significant excess of events with respect to the background prediction is observed corresponding to $3.1$ standard deviations for a Higgs mass hypothesis of $125~\GeV$. This result establishes evidence of the $125~\GeV$ Higgs boson decay to a pair of tau leptons. 

Additional searches for neutral resonances decaying to a pair of tau leptons in gluon-fusion and b-quark associated production modes are performed. No significant excess is observed and exclusion limits on the production cross section times branching ratios are given for neutral resonances with mass hypotheses ranging from $90~\GeV$ to $1~\TeV$. The results are also interpreted in the context of neutral Higgs boson production in the minimal supersymmetric extension of the Standard Model. 

Studies of the Standard Model Higgs boson pair production at the High-Luminosity LHC with an expected data sample corresponding to an integrated luminosity of $3000~\ifb$ are described. Higgs boson decays resulting in bb$\gamma\gamma$ and bb$\tau\tau$ final states are considered. These are the first detailed studies of the Higgs boson pair production assuming the expected performance of the upgraded CMS detector at the High-Luminosity LHC. The expected significance for the Standard Model Higgs boson pair production signal is $1.9$ standard deviations corresponding to an expected uncertainty of $54\%$ in the signal yield. 

The discovery of the new boson with a SM-like Higgs boson properties opens a new era towards our understanding of the fundamental interactions. The LHC will continue to explore the nature of the electroweak symmetry breaking in the coming years. Performing precise measurements of the observed SM-like Higgs boson is one of the main goals of the HL-LHC. Deviations from the SM predictions will provide hints on the BSM physics. Indeed, the SM theory of elementary particles has so far been remarkably successful in describing the present experimental observations. There are number of existing BSM theories, introduced to explain the limitations of the SM, patiently waiting for an opportunity to step forward. But perhaps, non of the existing BSM theories provides the correct fundamental equations describing nature. It is feasible that we will discover something unexpected that will guide us toward the ultimate theory of nature.

\epigraph{\textit{Who ordered that?}}{I. I. Rabi}


